Fast and optimal centroiding of faint stars

### 2015-11-04 ms/figure.tex
finished editing the first 3 pages

Given an analytic expression for the PSF model,
we derive an expression for the fundamental lower bound on the centroiding error as
a function of the parameters of the PSF model (\eg PSF size),
and signal-to-noise-ratio of stars. We create two sets of simulations for which we 
know the CRLB, one with variable (constant) signal-to-noise ratio (FWHM), and one 
with variable (constant) FWHM (signal-to-noise ratio). After applying
different centroiding methods to the simulations,
we investigate how close these methods can get to saturating the CRLB for
various ranges of background noise level and PSF FWHM.

>>>>

Given an analytic expression for the PSF model,
we derive an expression for the fundamental lower bound on the centroiding error as
a function of the parameters of the PSF model (\eg PSF size),
and signal-to-noise-ratio of stars. We create two sets of simulations for which we 
know the CRLB, one with variable signal-to-noise ratio and constant FWHM, and one 
with variable FWHM and constant signal-to-noise ratio. After applying
different centroiding methods to the simulations,
we investigate how close these methods can get to saturating the CRLB for
various ranges of background noise level and PSF FWHM.
